---
title: "Reproducible pitch presentation"
author: "Jan"
date: "March 24 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

- This app is intended to help you visualize the distribution of variables from different data sets by means of a histogram. 
- You are able to fit three different standard distributions (normal, exponential, uniform) to the data 
- The final results are then displayed over the histogram for a visual inspection of the fit.

## Input Parameters

- Data set: You can choose between three different data sets
- Number of bins: Here you can choose the number of bins the histogram should split the data into
- Distributions: Choose between normal, exponential or uniform distribution

## Calculation

A look into the server.R function:

```{r calc, echo = TRUE, eval=FALSE}
# switch data sets based on input data
switch(input$data_set, 
       "mtcars" = {
         xlab <- "Miles per Gallon"
         plot_data <- data.frame(x = mtcars$mpg)
       },
       "rivers" = {
         xlab <- "Lengths of Major North American Rivers (in miles)"
         plot_data <- data.frame(x = rivers)
       },
       "discoveries" = {
         xlab <- "Yearly Numbers of Important Discoveries"
         plot_data <- data.frame(x = as.numeric(discoveries))
       })

# draw the histogram with the specified number of bins
plot_data %>% ggplot(aes(x = x)) +
  geom_histogram(aes(y = ..density..), bins = input$bins) + 
  theme_bw() +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = xlab, y = "Frequency") +
  ggtitle(paste("Histogram of ", xlab)) -> plot

# add distributions
mean <- mean(plot_data$x)
sd <- sd(plot_data$x)
n <- nrow(plot_data)
min <- min(plot_data$x)
max <- max(plot_data$x)

if(input$dnorm){
  y_norm <- dnorm(plot_data$x, mean, sd)
  plot <- plot + geom_line(aes(x = plot_data$x, y = y_norm),
                           size = 1.4, color = "red")
}
if(input$dexp){
  y_exp <- dexp(plot_data$x, rate = 1/mean)
  plot <- plot + geom_line(aes(x = plot_data$x, y = y_exp),
                           size = 1.4, color = "blue")
}
if(input$dunif){
  y_unif <- dunif(plot_data$x, min = min, max = max)
  plot <- plot + geom_line(aes(x = plot_data$x, y = y_unif),
                           size = 1.4, color = "green")
}

plot
```

## Demo

The app can be found here: https://jmm-p.shinyapps.io/dddp_course_project/

This is an exemplary output for the discoveries data set with number of bins = 8 and the normal distribution:

```{r demo, echo=FALSE}

suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))

xlab <- "Yearly Numbers of Important Discoveries"
plot_data <- data.frame(x = as.numeric(discoveries))


# draw the histogram with the specified number of bins
plot_data %>% ggplot(aes(x = x)) +
  geom_histogram(aes(y = ..density..), bins = 8) + 
  theme_bw() +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = xlab, y = "Frequency") +
  ggtitle(paste("Histogram of ", xlab)) -> plot

# add distributions
mean <- mean(plot_data$x)
sd <- sd(plot_data$x)
n <- nrow(plot_data)
min <- min(plot_data$x)
max <- max(plot_data$x)


y_norm <- dnorm(plot_data$x, mean, sd)
plot <- plot + geom_line(aes(x = plot_data$x, y = y_norm),
                         size = 1.4, color = "red")


plot

```
    